### 2024-07-25 paper.tex
fill in part of proof for all-zero case.  also fix some notation

% \maketitle
\section{Definition of one thing}
Let \(G \subseteq \GL_m(\mathbb{C})\) be a connected semisimple Lie group, and let \(\mathfrak{g} \subseteq \gl_m(\mathbb{C})\) be its Lie algebra.
% ^I take this scope because it is about what Yuzhou Gu said.
Let \(\mathcal{N} \subseteq \mathfrak{g}\) be the subset consisting of nilpotent elements.
Let \(\mathcal{F}l\) be the variety of Borel subalgebras of \(\mathfrak{g}\).
Let \(\widetilde{\mathcal{N}} = \{(\mathfrak{m}, n) : n \in \mathfrak{m}\} \subseteq \mathcal{M} \times \mathcal{N}\).
Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the second coordinate.
For \(n \in \mathcal{N}\), we call \(\pi^{-1}(n)\) the \emph{Springer fiber at \(n\)}.

@@

\begin{lemma}

\end{lemma}

>>>>

% \maketitle
\section{Definition of one thing}
Let \(G \subseteq \GL_m(\mathbb{C})\) be a connected semisimple Lie group, and let \(\mathfrak{g} \subseteq \gl_m(\mathbb{C})\) be its Lie algebra.
% ^I take this scope because it is about what Yuzhou Gu said.
Let \(\mathcal{N} \subseteq \mathfrak{g}\) be the subset consisting of nilpotent elements.
Let \(\mathcal{B}\) be the variety of Borel subalgebras of \(\mathfrak{g}\).
Let \(\widetilde{\mathcal{N}} = \{(\mathfrak{b}, n) : n \in \mathfrak{b}\} \subseteq \mathcal{B} \times \mathcal{N}\).
Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N}\) be the projection onto the second coordinate.
For \(n \in \mathcal{N}\), we call \(\pi^{-1}(n)\) the \emph{Springer fiber at \(n\)}.

@@

\begin{lemma}
    Each \(\mathcal{F}_\delta\) is irreducible of dimension \(m\).
\end{lemma}
\begin{proof}
    Let \(\mathcal{E}\) be the variety of partial flags of \(E\) of shape \((\delta_0, ..., \delta_{n + 1})\).
    Define \(g : \mathcal{F}_\delta \to \mathcal{E}\) by
    \[(V, a, b) \mapsto 0 \subseteq V_{i_0} \cap E \subseteq V_{i_1} \cap E \subseteq \cdots \subseteq V_{i_{n + 1}} \cap E = E.\]
    It is clear that \(g\) is surjective, as the definition of \(\mathcal{F}_\delta\) places no restriction on the intersections \(V_i \cap E\).
    Now let's look more closely at the fibers \(g^{-1}(U)\).
    \par First let's find the flags \(V\) such that there exist \(a, b\) with \(g(V, a, b) = U\).
    We see that, for instance, \(V_{i_0} \cap E = U_1\).
    In fact \(V_{i_0} \subseteq E\), so \(V_{i_0} = U_1\).
    But we are free to choose the vector spaces between \(0\) and \(V_{i_0}\) however we wish, so we get some degrees of freedom like \(\mathcal{F}_{\delta_0}\), the complete flag variety on \(\mathbb{C}^{\delta_0} \cong V_{i_0} / 0\).
    Similarly, for every \(j = 1, ..., n + 1\), we can choose the vector spaces between \(V_{i_{j - 1}}\) and \(V_{i_j}\) arbitrarily, so we get degrees of freedom like \(\mathcal{F}_{\delta_{i_j}}\), the complete flag variety on \(\mathbb{C}^{\delta_{i_j}} \cong V_{i_j} / V_{i_{j - 1}}\).
    Finally, to meet the constraint of \((V, a, b)\) being in \(\mathcal{F}_\delta\), we can choose any \(b \in U_1\) and any \(a\) such that \(\overline{a} \in U_n^\perp\).
    Thus we get an isomorphism
    \[g^{-1}(U) \cong \mathcal{F}_{\delta_0} \times \cdots \times \mathcal{F}_{\delta_{n + 1}} \times \mathbb{C}^{\delta_0} \times \mathbb{C}^{\delta_{n + 1}}.\]

\begin{theorem}
    The \(\mathcal{F}_\delta\)'s are the irreducible components of \(\mathcal{F}\).
\end{theorem}
